Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-08-26 main.Rmd
cache removed from the code harmony-tab
Code styling

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
options("knitr.graphics.auto_pdf" = TRUE)
library(knitr)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = "figure/", fig.align = "center", fig.show = "hold",
  cache = TRUE, cache.path = "cache/",
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
#knitr::opts_knit$set(root.dir = here::here())
```

```{r external, include = FALSE, cache = FALSE}
read_chunk('scripts/main.R')
```

@@

```{r harmony-tab, echo=FALSE, cache=TRUE}
```

@@

```{r write-bib, eval = FALSE}
write_bib(c("rmarkdown", "bookdown", "rticles", "knitr", "ggplot2", "dplyr", "tsibble", "gravitas", "ggpubr", "kableExtra", "magrittr"), file = "rpkgs.bib")
```

>>>>

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
options("knitr.graphics.auto_pdf" = TRUE)
library(knitr)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = "figure/", fig.align = "center", fig.show = "hold",
  cache = TRUE, cache.path = "cache/",
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
# knitr::opts_knit$set(root.dir = here::here())
```

```{r external, include = FALSE, cache = FALSE}
read_chunk("scripts/main.R")
```

@@

```{r harmony-tab, echo=FALSE}
```

@@

```{r write-bib, eval = FALSE}
write_bib(c("rmarkdown", "bookdown", "rticles", "knitr", "ggplot2", "dplyr", "tsibble", "gravitas", "ggpubr", "kableExtra", "magrittr", "readr", "lubridate", "renv", "archive"), file = "rpkgs.bib")
```
